---
title: "PA4-ds4ling"
author: "Chaoyi Chen"
institute: "Rutgers University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["hygge", "rutgers", "rutgers-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

- Load the dataset from your index.Rmd file.
```{r}
fricatives <- read.csv("~/Desktop/pa4/data_raw/fricatives/fricatives.csv") # load the dataset
fricatives # show the dataset
```
---
- Tidy the data and save the tidy version as a .csv file in data_tidy.
```{r, warnings=F, message=F,out.width="50%"}                      
library(tidyverse)
fricatives_tidy <- pivot_longer(fricatives,c(`s_cog`:`sh_skewness`), names_to = "category", values_to = "values") %>% # turn the four categories into one column
  separate(category, into = c("phoneme", "kind"), sep = "_") %>% # separate phoneme and kind
  pivot_wider(names_from = kind, values_from = values) # put cog and skewness back to columns
fricatives_tidy # show the tidy version
write.csv(fricatives_tidy,"~/Desktop/pa4/data_tidy/fricatives_tidy.csv") # save the tidy version as a .csv file in data_tidy
```
---
- Provide a table of descriptive statistics.
```{r, warnings=F, message=F,fig.align='center'}
summary(fricatives_tidy)
```

---
- Make a boxplot of center of gravity as a function of phoneme.
```{r,fig.width=8,fig.height=5,fig.align='center'}
fricatives_tidy %>% 
  ggplot(., mapping = aes(x = phoneme, y = cog)) +
  geom_boxplot() +
  stat_summary(mapping = aes(x = phoneme, y = cog),fun.min = min, fun.max = max, fun = median)
```


---
- Plot skewness as a function of phoneme.
```{r,fig.width=8,fig.height=5,fig.align='center'}
fricatives_tidy %>% 
  ggplot(., mapping = aes(x = phoneme, y = skewness)) +
  geom_boxplot() +
  stat_summary(mapping = aes(x = phoneme, y = skewness),fun.min = min, fun.max = max, fun = median)
```
---
- Fit a model that examines center of gravity as a function of skewness for the [s] segments. Make a table of the model summary.
```{r}
q8 <- filter(fricatives_tidy, phoneme == "s") # data transformation : pick out [s] data
  lm(formula = cog ~ skewness, data = q8) %>% # fit a model
  summary() # make a table
```
---
- Make a scatter plot that illustrates the relationship in (8).
```{r,fig.width=8,fig.height=5,fig.align='center'}
q8 %>% 
  ggplot(., mapping = aes(x = skewness, y = cog)) +
  geom_point() +
  geom_smooth(method = lm)
```
---
# Check model diagnostics (1) 
- Check the general pattern: the plot shows that the relationship between x and y is basically linear.

```{r,fig.width=8,fig.height=5,echo=FALSE, message=FALSE, fig.align='center'}
q8 %>% 
  ggplot(., mapping = aes(x = skewness, y = cog)) +
  geom_point() +
  geom_smooth(method = lm)
```

---
# Check model diagnostics (2) 
- Check the mean of residuals: the mean of residuals is 1.136591e-14, which is almost equal to zero.
```{r}

q10 <- lm(formula = cog ~ skewness, data = q8)
mean(q10$residuals)
```
---
# Check model diagnostics (3)

Check homoskedasticity and normal distribution: the variance around predicted values is consistent and the distribution of residuals is basiclly normal.

```{r,fig.width=8,fig.height=5, message=FALSE, warning = FALSE,fig.align='center'}
ds4ling::diagnosis(q10)
```
---
# Check model diagnostics (4) 
- Check the uncorrelation between predictors and residuals: Cor.test is used to test whether predictor and residuals are correlated or not. The returned p-value is 1 and the null hypothesis cannot be rejected.

```{r}
cor.test(q8$skewness, q10$residuals)
```
---
# Check model diagnostics (5) 

Check no autocorrelation of residuals: the p-value of Runs test is 0.3581, which is larger than 0.05, thus we can maintain the hypothesis that there is no autocorrelation of residuals.

```{r,fig.width=8,fig.height=5, message=FALSE, warning = FALSE,fig.align='center'}

library("lawstat")
lawstat::runs.test(q10$residuals)
```
---
# Write up the results

This study checked the regression assumptions of the current model and it turns out that all assumptions are satisfied. 

The model specification assumption is satisfied. The plot in (1) shows that the relationship between x and y is basically linear. 

The error term assumptions are also satisfied. (2) displays that the mean of residuals is almost equal to 0. The first plot of (3) illustrates that the variance around predicted values is consistent, and the homoskedasticity of residuals is confirmed. The second and third plot of (3) exhibit that the residuals are basically normally distributed. (4) uses the function of cor.test to test if predictor and residuals are correlated. The returned p-value is 1, which is much larger than 0.05, thus we cannot reject the null hypotheses that true correlation is equal to 0 and conclude that predictor and residuals are not correlated. The p-value of runs-test in (5) confirms that there is no autocorrelation of residuals.


